---
title: "Lab3_StatisticalSloths"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

Overall question, why it’s important, and why that’s important
## What is the relationship between general health and smoking controlling for gender? 
* This is an interesting question because the answer could help us to find a better understand of how smoking impacts one's general health and well being, specifically looking at males and females. This is important because knowing this may help to discourage people from continuing to smoke or starting smoking, and encourage those who want to improve their general well being to stop smoking. 

(TEAM PLOT HERE ) *Check that this has all the requirments

```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = gender, fill= genhlth)) +
  facet_grid(smoke100~genhlth)+
  ggtitle('General Health vs. Smoking')
```


###Our Findings

Our team saw that for both men and women there were more people that had excellent health that were non-smokers than those who did smoke. More people had poor health if they did smoke than those who did not. In general more men smoked than women.

###Our Conclusions 

*Fill in conclusions here*


###Our Reccomendation 

*Fill in Recommendation "A “Recommendation” is a suggested action or series of actions. For this lab report, we will assume that your team has been hired by the Centers for Disease Control and Prevention (CDC) to analyze their 2000 dataset to answer your overall question and make a recommendation for a change in policy. You may use your creativity in this case to recommend new policy or perhaps your recommendation will be to analyze new data. If that’s the case, be specific about what new question your new analyses would attempt to answer."*


Madeline's PLot

Madeline's Finding's

```{r}
ggplot(data = cdc) + 
  geom_bar(mapping = aes(x = smoke100, fill = genhlth), position = "fill")
```




Zandy Plot 
```{r}
ggplot(data = cdc) +
geom_bar(mapping = aes(x = age, fill = genhlth
```

Katie Plot 

```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = age, fill = genhlth)) +
  facet_grid(smoke100~genhlth)

```


Kevin's Plot 
```{r}
ggplot(data = cdc) + 
  geom_jitter(mapping = aes(x = genhlth, y = age, color = genhlth)) + 
  facet_wrap(~ exerany) + 
  xlab("General Health") + 
  ylab("Age") + 
  theme(axis.text.x = element_text(angle=17))
```
Kevin's Findings: 
I, Kevin Luth, created a plot showing how general health and exercise are related and whether age affects this relationship. The data showed that regardless of age, there is a distinct difference in the general health levels of those who have exercised in the last month and those who have not. There are more people reporting better health levels and less reporting poor health levels among those who have exercised. I used the geom_jitter function and adjusted the color of the general health levels. In addition I used the facet_wrap function to clearly display the difference in the levels of those who exercise and those who do not. I also rotated the x tick mark labels so that they did not overlap and I changed the axis labels to the full word and not just the abbreviations.


The summary of who did what.

* I, Katie Stewart, created a plot showing how general health and smoking were related and how they differ between age groups. The data showed that those who smoke and are over the age of around 40 are more susceptible to having poor or fair health. I used the geom_bar function to create my graph and added a color fill. I also used the facet_grid function to make it easier to distinguish between those who smoke and those who do not among there age groups. 
