---
title: "Lab3_StatisticalSloths"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

Overall question, why it’s important, and why that’s important
## What is the relationship between weight and height controlling for effects of the general health and smoking coverage? 
* This question is important because ... and this is important because...

(TEAM PLOT HERE )
```{r}
ggplot(data = cdc) + 
  geom_jitter(mapping = aes(x = height, y = weight, color= genhlth)) + 
  facet_grid(smoke100~genhlth)
```

Answer to the overall question and our teams recommendation



A series of findings and plots (individual parts of the lab)
INDIVIDUAL PLOTS 

Madeline PLot 

```{r}
ggplot(data = cdc) + 
  geom_bar(mapping = aes(x = smoke100, fill = genhlth), position = "fill")
```




Zandy Plot 
ggplot(data = cdc) +
geom_bar(mapping = aes(x = age, fill = genhlth


Katie Plot 

```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = gender, color = genhlth)) +
  facet_grid(smoke100~genhlth)
```


Kevin Plot 
```{r}
ggplot(data = cdc) + 
  geom_bar(mapping = aes(x = genhlth), color = "orange") + 
  facet_grid( ~ exerany)
```



The summary of who did what.



